---
title: "test-data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# packakages
```{r, include=FALSE}
install.packages("iriR")
install.packages("tidyr")
install.packages("dplyr")
install.packages("readxl")
install.packages("ggplot2")
install.packages("ggthemes")
install.packages("MASS")
install.packages("stargazer")
install.packages("gsheet")
install.packages("gtsummary")
```

```{r, include=FALSE}
library(iriR)
library(tidyr)
library(dplyr)
library(readxl)
library(ggplot2)
library(ggthemes)
library(MASS)
library(stargazer)
library(gsheet)
library(gtsummary)
```

# data cleaning:

```{r, include=FALSE}

data_test2 <- irir_data(,indicators = "RD.intensity")
data_test2$RD_intensity <- data_test2$value
data_test2$indicator_code <- NULL
data_test2$value <- NULL

excel <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1LvrUVtUihRWMHgDqLAJHVm7_VeAqWBEZ7d1I3nAwD8U/edit?usp=sharing")

```


```{r, include=FALSE}
final_data <- data_test2

final_filtered_data <- filter(final_data,year == "2019", rank < 31)
final_filtered_data$geographical_loc <- excel$geografical_location
final_filtered_data$indicator <- excel$Y_variable
final_filtered_data$patents_2018 <- excel$pantents_2018 /1000

final_filtered_data <- final_filtered_data %>% mutate(indicator = case_when(indicator == "top 10" ~ 2, indicator == "top 20" ~ 1, TRUE ~ 0))

final_filtered_data$indicator <- as.ordered(final_filtered_data$indicator)

Keila_data <- filter(final_data,year==2019)




```

# data description:

## R&D intensity:
```{r}
summary(final_filtered_data$RD_intensity)
hist(final_filtered_data$RD_intensity)
```
## pantens in 2018:
```{r}
summary(final_filtered_data$patents_2018)
hist(final_filtered_data$patents_2018)
```



# data visualization: 


```{r}
table_keila <- table(Keila_data$country_code,Keila_data$year)

table_keila
```


```{r}
ggplot(data = final_filtered_data, aes(x = country_code, fill = country_code)) + 
  geom_bar() +
  xlab("") +
  ylab("Number of company in the top 30")  +
  labs(fill = "County code")  +  
  theme_minimal() + 
  scale_fill_brewer(direction = 1)
```

```{r}
ggplot(data = final_filtered_data, aes(x = geographical_loc, fill = geographical_loc)) + 
  geom_bar() +
  xlab("") +
  ylab("Number of company in the top 30")  +
  labs(fill = "Geographical location")  +  
  theme_minimal() + 
  scale_fill_brewer(direction = 1)
```



# model 
```{r}
str(final_filtered_data)
```


```{r}
ftable(xtabs(~ indicator + RD_intensity + patents_2018, data = final_filtered_data))
```


## model1 => indicator = r&d intensity + patent 2018
```{r}
model1 <- polr(indicator ~ RD_intensity + patents_2018, data = final_filtered_data, Hess=TRUE)

summary(model1)
table1 <- coef(summary(model1))
p1 <- pnorm(abs(table1[, "t value"]), lower.tail = FALSE) * 2
(table1 <- cbind(table1, "p value" = p1))
```
 
```{r}
# (Nic) trying to find residuals, using source, but it gives me "NULL"
# Source: https://rdrr.io/rforge/regr0/man/residuals.polr.html
model1.resid <- residuals(model1)
head(model1.resid)
summary(model1.resid)
```
 
## model2 => indicator = (r&d intensity)**2 + patent 2018
```{r}
model2 <- polr(indicator ~ (RD_intensity)**2 + patents_2018, data = final_filtered_data, Hess=TRUE)

summary(model2)

table2 <- coef(summary(model2))
p2 <- pnorm(abs(table2[, "t value"]), lower.tail = FALSE) * 2
(table2 <- cbind(table2, "p value" = p2))
```


## model3 => indicator = r&d intensity + (patent 2018)**2
```{r}
model3 <- polr(indicator ~ RD_intensity + (patents_2018)**2, data = final_filtered_data, Hess=TRUE)

summary(model3)
table3 <- coef(summary(model3))
p3 <- pnorm(abs(table3[, "t value"]), lower.tail = FALSE) * 2
(table3 <- cbind(table3, "p value" = p3))
```
## model4 => indicator = r&d intensity * patent
```{r}
model4 <- polr(indicator ~ RD_intensity * patents_2018, data = final_filtered_data, Hess=TRUE)

summary(model4)
table4 <- coef(summary(model4))
p4 <- pnorm(abs(table4[, "t value"]), lower.tail = FALSE) * 2
(table4 <- cbind(table4, "p value" = p4))
```



# odds
```{r}
exp(coef(model1))
```
## r&d intensity:
For every one unit increase in R&D intensity, the odds of being in the upper rank  (top 10 or top 20  versus top 30) is multiplied 0.94 times, holding constant all other variables.

For every one unit decrease in R&D intensity, the odds of being in the lower rank (top 30 versus top 20 or top 10) is multiplied 0.94 times, holding constant all other variables.

## pantent:
For every one unit increase in patent, the odds of being in the upper rank (top 10 or top 20 versus top 30) is multiplied 2.06 times, holding constant all other variables.

For every one unit decrease in patent, the odds of being in the lower rank (top 30 versus top 20 or top 10) is multiplied 2.06 times, holding constant all other variables.

```{r}
exp(coef(model4))
```
## r&d intensity:
For every one unit increase in R&D intensity, the odds of being in the upper rank  (top 10 or top 20  versus top 30) is multiplied 0.93 times, holding constant all other variables.

For every one unit decrease in R&D intensity, the odds of being in the lower rank (top 30 versus top 20 or top 10) is multiplied 0.93 times, holding constant all other variables.

## pantent:
For every one unit increase in patent, the odds of being in the upper rank (top 10 or top 20 versus top 30) is multiplied 1.89 times, holding constant all other variables.

For every one unit decrease in patent, the odds of being in the lower rank (top 30 versus top 20 or top 10) is multiplied 1.89 times, holding constant all other variables.

## interaction:
For every one unit increase in the interaction variable, the odds of being in the upper rank (top 10 or top 20 versus top 30) is multiplied 1.007 times, holding constant all other variables.

For every one unit decrease in the interaction variable, the odds of being in the lower rank (top 30 versus top 20 or top 10) is multiplied 1.007 times, holding constant all other variables.

